Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 10:14

These values were determined through the implementation of an empirical method with
manual inspection of the CE identification results  on selected days of the whole
dataset.  We used seven sets of days with characteristics relevant to the efficiency
of the identification threshold.  These sets were random groups of about 20 -- 30
days with the following characteristics:
(a) the strongest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) absence of clouds and absence of EC events,
(e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
(h) randomly selected days and
(i) manually selected days.
Where needed in some of the edge cases, we also used images from a sky-camera
to further aid the decision of the manual inspection.

@@

The definition of the CE events with this method has a degree of subjectivity, since
the actual clear sky irradiance, is not known, and can only be approximated.
However, this method is capable in detecting all major CE events.  Where, some CE
events, with very low OIR may be not detected, these are few with small
over-irradiance and it is unlikely that will effect significantly our results.

<!-- extreme cases criterion -->
A sub-category  of the CE events that is often discussed in the relevant bibliography,
are cases of extreme cloud enhancement (ECE). These are cases of CE, where the
measured intensity of the irradiance, exceeds the equivalent TSI on the top of the
atmosphere, and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant, $r$ the Sun -- Earth distance, and $i$ each of the one-minute observation.

To give a better understanding of the CE identification procedure, we provided an
example of the CE identification for a selected day, in the Appendix
(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the clear sky
reference and the identification threshold are shown, along with the relevant
measurements.  Similar, we provided an example plot of data for one year, where the
relation of the GHI and clear sky reference is shown, along with the OIR intensity
(Appendix Figure\nobreakspace{}\ref{fig:example-year}).

@@

```{r example-day, echo=FALSE, fig.cap="Example of cloud identification data for 2019-07-11. Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.", fig.pos='H'}
knitr::include_graphics("../images/example-days-18.png")
```

>>>>

These values were determined through the implementation of an empirical method with
manual inspection of the CE identification results  on selected days of the whole
dataset.  We used seven sets of days with characteristics relevant to the efficiency
of the identification threshold.  These sets were random groups of about 20 -- 30
days with the following characteristics:
(a) the strongest over irradiance CE events,
(b) the largest daily total over irradiance,
(c) absence of clouds (by implementing a clear sky identification algorithm as discussed in @Natsis2023),
(d) absence of clouds and absence of EC events,
(e) with at least $60\,\%$ of the day length without clouds and presence of EC events,
(h) randomly selected days, and
(i) manually selected days.
Where needed in some of the edge cases, we also used images from a sky-camera
to further aid the decision of the manual inspection.

@@

The definition of the CE events with this method has a degree of subjectivity, since
the actual clear sky irradiance, is not known and can only be approximated.
However, this method is capable in detecting all major CE events.  Where, some CE
events, with very low OIR may be not detected, these are few with small
over-irradiance and it is unlikely that will effect significantly our results.

<!-- extreme cases criterion -->
A sub-category  of the CE events that is often discussed in the relevant bibliography
[@Cordero2023; @Martins2022; @Yordanov2015], are the extreme cloud enhancement (ECE)
events. These are cases of CE where the measured intensity of the irradiance, exceeds
the TSI at the top of the atmosphere:
<!--and detected according to the Equation\nobreakspace{}\ref{eq:ECE}.-->
\begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation}
where: $\theta$ the solar zenith angle, $E_{\odot}$ the solar constant adjusted for the actual Sun -- Earth distance, and $i$ each of the one-minute observation.

An example of CE identification for a selected day is given, in the Appendix
(Figure\nobreakspace{}\ref{fig:example-day}), where the clear sky reference
irradiance and the CE and ECE identification thresholds are shown along with the
actual GHI measurements.  Similar, we provided an example plot of data for one year,
where the relation of the GHI and clear sky reference is shown, along with the OIR
intensity (Appendix Figure\nobreakspace{}\ref{fig:example-year}).

```{r example-day, echo=FALSE, fig.cap="Example of cloud identification for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles. The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.", fig.pos='H'}
knitr::include_graphics("../images/example-days-18.png")
```

@@

### 2024-06-11 article/article.tex
Commit 2024-06-11 10:14

These values were determined through the implementation of an empirical
method with manual inspection of the CE identification results on
selected days of the whole dataset. We used seven sets of days with
characteristics relevant to the efficiency of the identification
threshold. These sets were random groups of about 20 -- 30 days with the
following characteristics: (a) the strongest over irradiance CE events,
(b) the largest daily total over irradiance, (c) absence of clouds (by
implementing a clear sky identification algorithm as discussed in
\citet{Natsis2023}), (d) absence of clouds and absence of EC events, (e)
with at least \(60\,\%\) of the day length without clouds and presence
of EC events, (h) randomly selected days and (i) manually selected days.
Where needed in some of the edge cases, we also used images from a
sky-camera to further aid the decision of the manual inspection.

The definition of the CE events with this method has a degree of
subjectivity, since the actual clear sky irradiance, is not known, and
can only be approximated. However, this method is capable in detecting
all major CE events. Where, some CE events, with very low OIR may be not
detected, these are few with small over-irradiance and it is unlikely
that will effect significantly our results.

A sub-category of the CE events that is often discussed in the relevant
bibliography, are cases of extreme cloud enhancement (ECE). These are
cases of CE, where the measured intensity of the irradiance, exceeds the
equivalent TSI on the top of the atmosphere, and detected according to
the Equation\nobreakspace{}\ref{eq:ECE}. \begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant, \(r\) the Sun -- Earth distance, and \(i\) each of
the one-minute observation.

To give a better understanding of the CE identification procedure, we
provided an example of the CE identification for a selected day, in the
Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the use of
the clear sky reference and the identification threshold are shown,
along with the relevant measurements. Similar, we provided an example
plot of data for one year, where the relation of the GHI and clear sky
reference is shown, along with the OIR intensity (Appendix
Figure\nobreakspace{}\ref{fig:example-year}).

@@

\caption{Example of cloud identification data for 2019-07-11. Where are denoted with red circles all the detected CE events, the cloud interaction with the GHI (blue crosses), and the thresholds of CE and the threshold of ECE events with red and black line respectively.}\label{fig:example-day}
\end{figure}

>>>>

These values were determined through the implementation of an empirical
method with manual inspection of the CE identification results on
selected days of the whole dataset. We used seven sets of days with
characteristics relevant to the efficiency of the identification
threshold. These sets were random groups of about 20 -- 30 days with the
following characteristics: (a) the strongest over irradiance CE events,
(b) the largest daily total over irradiance, (c) absence of clouds (by
implementing a clear sky identification algorithm as discussed in
\citet{Natsis2023}), (d) absence of clouds and absence of EC events, (e)
with at least \(60\,\%\) of the day length without clouds and presence
of EC events, (h) randomly selected days, and (i) manually selected
days. Where needed in some of the edge cases, we also used images from a
sky-camera to further aid the decision of the manual inspection.

The definition of the CE events with this method has a degree of
subjectivity, since the actual clear sky irradiance, is not known and
can only be approximated. However, this method is capable in detecting
all major CE events. Where, some CE events, with very low OIR may be not
detected, these are few with small over-irradiance and it is unlikely
that will effect significantly our results.

A sub-category of the CE events that is often discussed in the relevant
bibliography \citep{Cordero2023, Martins2022, Yordanov2015}, are the
extreme cloud enhancement (ECE) events. These are cases of CE where the
measured intensity of the irradiance, exceeds the TSI at the top of the
atmosphere: \begin{equation}
\text{ECE}: \text{GHI}_\text{i} > \cos(\theta) \times E_{i\odot} / r_{i}^2
\label{eq:ECE}
\end{equation} where: \(\theta\) the solar zenith angle, \(E_{\odot}\)
the solar constant adjusted for the actual Sun -- Earth distance, and
\(i\) each of the one-minute observation.

An example of CE identification for a selected day is given, in the
Appendix (Figure\nobreakspace{}\ref{fig:example-day}), where the clear
sky reference irradiance and the CE and ECE identification thresholds
are shown along with the actual GHI measurements. Similar, we provided
an example plot of data for one year, where the relation of the GHI and
clear sky reference is shown, along with the OIR intensity (Appendix
Figure\nobreakspace{}\ref{fig:example-year}).

\caption{Example of cloud identification for 2019-07-11. The green line with blue symbols depicts the measured GHI in one minute steps. The red line shows the modelled threshold for the detection of CE events, which are denoted with red circles. The black curve represents the TSI at the top of the atmosphere, adjusted for the actual Sun-Earth distance and multiplied by the cosine of the cosine of SZA.}\label{fig:example-day}
\end{figure}

@@
